---
title: "Replication 2 Megan Ellertson"
author: "Megan Ellertson"
date: "4/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Replication 2
```{r}
library(tidyverse)
library(haven)
library(stargazer)
library(foreign)
```
*The data combined was completed in STATA then brought into R for quicker computation. See the following STATA syntax, which was used to create the combined and used data set for the analysis.*


```{r}

dataset <- read.dta("Replication -2-/Data/combineddata.dta")
```

```{r}
nsw_dw_cpscontrol <- dataset %>% 
  mutate(agesq = age^2,
         agecube = age^3,
         educsq = educ*educ,
         u74 = case_when(re74 == 0 ~ 1, TRUE ~ 0),
         u75 = case_when(re75 == 0 ~ 1, TRUE ~ 0),
         interaction1 = educ*re74,
         re74sq = re74^2,
         re75sq = re75^2,
         interaction2 = u74*hisp)
#Creating logit data 
nsw_dw_cpscontrol_logit <- nsw_dw_cpscontrol %>%
  mutate(educcube = educ^3,
         re74cube=re74^3, 
         re75cube=re75^3)
#Creating ols data
nsw_dw_cpscontrol_ols <- nsw_dw_cpscontrol %>%
  mutate(re74quad = re74^4,
         re75quad = re74^4)
```

1a.
The following equations are for the logit and OLS versions of the basic equation provided in the mixtape nsq_pscore.do. This expands off the basic logit provided. 
$$logit(treat)= age + age^2 + age^3 + educ + educ^2 + + educ^3 +marr + nodegree + black + 
hisp + re74 + re74^2 + re74^3 + re75 + re75^2 + re75^3 + u74 + u75 + educ*hisp + \epsilon$$
```{r}
logit <- glm(treat ~ age + agesq + agecube + educ + educsq
                     + educcube + marr + nodegree
                     + black + hisp + re74 + re74sq + re74cube 
                     + re75 + re75sq + re75cube + u74 + u75 +
                       interaction1, family = binomial(link =
                      "logit"), data = nsw_dw_cpscontrol_logit)
```
$$ols(treat) = age + age^2 + educ + educ^2 + marr + nodegree + black + 
hisp + re74 + re74^2 + re75 + re75^2 + u74 + u75 + educ*hisp + \epsilon$$

```{r}
ols <- lm(treat ~ age + agesq + agecube + educ + marr + 
                    nodegree+ black + hisp + re74 + re74sq
                     + re75 + re75sq + u74 + u75 + interaction1,
                  data = nsw_dw_cpscontrol_ols)
```
The following table provides the output of both the OLS and the Logit regression estimates from the equations above. 
```{r}
stargazer(ols, logit, 
          type = "html",
          title = ,
          column.labels = c(""),
          colnames = FALSE,
          covariate.labels = c(""),
          keep.state = c("rsq", "f"),
          )
```

```{r}
nsw_dw_cpscontrol_logit <- nsw_dw_cpscontrol_logit %>% 
  mutate(pscore = logit$fitted.values)


nsw_dw_cpscontrol_ols <- nsw_dw_cpscontrol_ols %>% 
  mutate(pscore = ols$fitted.values)
```


```{r}
pscore_control_logit <- nsw_dw_cpscontrol_logit %>%
  filter(treat==0) %>%
  pull(pscore) %>%
  mean()
pscore_control_logit <- nsw_dw_cpscontrol_logit %>%
  filter(treat==1) %>%
  pull(pscore) %>%
  mean()

pscore_control_ols <- nsw_dw_cpscontrol_ols %>%
  filter(treat==0) %>%
  pull(pscore) %>%
  mean()
pscore_control_ols <- nsw_dw_cpscontrol_ols %>%
  filter(treat==1) %>%
  pull(pscore) %>%
  mean()
```
1.c. The following are the histograms for the mean p-scores of the logit and ols models for both models treated and untreated groups. 
```{r}
nsw_dw_cpscontrol_logit %>% 
  filter(treat == 0) %>% 
  ggplot() +
  geom_histogram(aes(x = pscore))

nsw_dw_cpscontrol_logit %>% 
  filter(treat == 1) %>% 
  ggplot() +
  geom_histogram(aes(x = pscore))
```

```{r}

nsw_dw_cpscontrol_ols %>% 
  filter(treat == 0) %>% 
  ggplot() +
  geom_histogram(aes(x = pscore))

nsw_dw_cpscontrol_ols %>% 
  filter(treat == 1) %>% 
  ggplot() +
  geom_histogram(aes(x = pscore))
```
DISCUSS THE SHAPE AND DISTRIBUTIONMN AND MAX VALUES FOR TREATMENT GROUP AND THE CONTROL GROUPS. 
1.d. The pscores which are less than 0.1 and greater than 0.9 can then be dropped and the histograms recalibarated with the trimmed pscores. 
```{r}
nsw_dw_cpscontrol_logit <- nsw_dw_cpscontrol_logit %>% 
  filter(!(pscore >= 0.9)) %>% 
  filter(!(pscore <= 0.1))

Nl <- nrow(nsw_dw_cpscontrol_logit)

nsw_dw_cpscontrol_ols <- nsw_dw_cpscontrol_ols %>% 
  filter(!(pscore >= 0.9)) %>% 
  filter(!(pscore <= 0.1))

No <- nrow(nsw_dw_cpscontrol_ols)
```

```{r}

pscore_control_logit <- nsw_dw_cpscontrol_logit %>%
  filter(treat==0) %>%
  pull(pscore) %>%
  mean()
pscore_control_logit <- nsw_dw_cpscontrol_logit %>%
  filter(treat==1) %>%
  pull(pscore) %>%
  mean()

pscore_control_ols <- nsw_dw_cpscontrol_ols %>%
  filter(treat==0) %>%
  pull(pscore) %>%
  mean()
pscore_control_ols <- nsw_dw_cpscontrol_ols %>%
  filter(treat==1) %>%
  pull(pscore) %>%
  mean()
```

```{r}
nsw_dw_cpscontrol_logit %>% 
  filter(treat == 0) %>% 
  ggplot() +
  geom_histogram(aes(x = pscore))

nsw_dw_cpscontrol_logit %>% 
  filter(treat == 1) %>% 
  ggplot() +
  geom_histogram(aes(x = pscore))
```

```{r}

nsw_dw_cpscontrol_ols %>% 
  filter(treat == 0) %>% 
  ggplot() +
  geom_histogram(aes(x = pscore))

nsw_dw_cpscontrol_ols %>% 
  filter(treat == 1) %>% 
  ggplot() +
  geom_histogram(aes(x = pscore))
```
DESCRIBE THE SHAPE OF THE HISTOGRAMS, THE MIN AND MAX VALUES OF BOTH THE CONTROL AND TREATMENT GROUP. 

The following is the 
```{r}
#- Manual with non-normalized weights using trimmed data Logit
nsw_dw_cpscontrol_logit <- nsw_dw_cpscontrol_logit %>% 
  mutate(d1 = treat/pscore,
         d0 = (1-treat)/(1-pscore))

s1 <- sum(nsw_dw_cpscontrol_logit$d1)
s0 <- sum(nsw_dw_cpscontrol_logit$d0)

nsw_dw_cpscontrol_logit <- nsw_dw_cpscontrol_logit %>% 
  mutate(y1 = treat * re78/pscore,
         y0 = (1-treat) * re78/(1-pscore),
         ht = y1 - y0)

#- Manual with normalized weights with trimmed data
nsw_dw_cpscontrol_logit <- nsw_dw_cpscontrol_logit %>% 
  mutate(y1 = (treat*re78/pscore)/(s1/Nl),
         y0 = ((1-treat)*re78/(1-pscore))/(s0/Nl),
         norm = y1 - y0)

nsw_dw_cpscontrol_logit %>% 
  pull(ht) %>% 
  mean()

nsw_dw_cpscontrol_logit %>% 
  pull(norm) %>% 
  mean()
```

```{r}
#- Manual with non-normalized weights using trimmed data OLS
nsw_dw_cpscontrol_ols <- nsw_dw_cpscontrol_ols %>% 
  mutate(d1 = treat/pscore,
         d0 = (1-treat)/(1-pscore))

s1 <- sum(nsw_dw_cpscontrol_ols$d1)
s0 <- sum(nsw_dw_cpscontrol_ols$d0)

nsw_dw_cpscontrol_ols <- nsw_dw_cpscontrol_ols %>% 
  mutate(y1 = treat * re78/pscore,
         y0 = (1-treat) * re78/(1-pscore),
         ht = y1 - y0)

#- Manual with normalized weights with trimmed data
nsw_dw_cpscontrol_ols <- nsw_dw_cpscontrol_ols %>% 
  mutate(y1 = (treat*re78/pscore)/(s1/No),
         y0 = ((1-treat)*re78/(1-pscore))/(s0/No),
         norm = y1 - y0)

nsw_dw_cpscontrol_ols %>% 
  pull(ht) %>% 
  mean()

nsw_dw_cpscontrol_ols %>% 
  pull(norm) %>% 
  mean()
```

